---
title: "Penguins"
author: "Mia Fitzgerald"
date: "4/21/2026"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(knitr)
library(tidyverse)
library(readxl)
library(DBI)
library(dbplyr)
library(duckdb)

```


### Loading Three Worksheets


```{r, class.source = 'fold-show'}
penguins_t_xl <- read_excel("penguins.xlsx", sheet = "Torgersen Island", na = "NA")
penguins_b_xl <- read_excel("penguins.xlsx", sheet = "Biscoe Island", na = "NA")
penguins_d_xl <- read_excel("penguins.xlsx", sheet = "Dream Island", na = "NA")

```


I am using the read_excel function to import three specific sheets—Torgersen, Biscoe, and Dream Island—from a single Excel workbook. By setting na = "NA", I ensure that any text entries labeled "NA" are converted into true missing values so they don't interfere with my future calculations. Finally, I am assigning each sheet to its own unique tibble so I can store and organize the data within my R environment.
^[Question 1 complete]


### Stacking the Three Worksheets


```{r, class.source = 'fold-show'}
combined_penguins <- bind_rows(penguins_b_xl, penguins_d_xl, penguins_t_xl)

```


I am using the bind_rows() function to stack the three individual island tibbles—Biscoe, Dream, and Torgersen—into a single master dataset.
^[Question 2 complete]


### Bill Depth Versus Bill Length by Island


```{r}
combined_penguins %>%
  ggplot(aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
  geom_point() + 
  facet_wrap(~island)

```


I am creating a scatter plot to visualize the relationship between penguin bill depth and bill length across the three islands. By using aes(color = species), I am assigning a unique color to each species so I can easily distinguish between them on the plot.
^[Question 3 complete]


### Average Body Masses for the Different Penguin Species


```{r}
combined_penguins %>%
  select(species, body_mass_g) %>%
  group_by(species) %>%
  summarize(avg_body_mass = mean(body_mass_g, na.rm = TRUE)) %>%
  kable() 

```


I first select only the species and body mass columns, then group the data by species to calculate the average body mass while ignoring any missing values. Finally, I use the kable() function to convert the resulting data into a professional-looking table suitable for a report or document.
^[Question 4 complete]


### Started a New, Temporary DuckDB Database


```{r, class.source = 'fold-show'}
con <- DBI::dbConnect(duckdb::duckdb())

```


In this line, I am establishing a connection to a new, temporary DuckDB database that lives entirely in my computer's RAM.
^[Question 5 complete]


### Tibble to the Database


```{r, class.source = 'fold-show'}
dbWriteTable(con, "combined_penguins", combined_penguins)

```


I am taking the combined_penguins tibble from my R environment and writing it into the DuckDB database as a table.
^[Question 6 complete]


### dbplyr Connection to Penguins DB table


```{r}
combined_penguins_db <- tbl(con, "combined_penguins")
combined_penguins_db %>% 
  collect() 

```


I am creating a dbplyr reference that points R to the specific table inside my database. In the second line, I use collect() to force R to actually download that data from the database and bring it into my local environment as a usable table.
^[Question 7 complete]


### SQL Query of Using the DB to Calculate the Average Body Masses for the Different Penguin Species


```{r}
combined_penguins_db %>%
  select(species, body_mass_g) %>%
  group_by(species) %>%
  summarize(avg_body_mass = mean(body_mass_g, na.rm = TRUE)) %>%
  show_query()

```


I am using dbplyr to perform a calculation entirely within the database. I first select the species and body mass columns, group them by species, and calculate the average mass. Finally, by using show_query(), I am asking R to display the underlying SQL code it generated to talk to the database instead of showing the actual data results.
^[Question 8 complete]
